Robustness of MinD oscillation in \emph{Escherichia coli} with diverse cell shapes

### 2014-08-11 paper/paper.tex
made changes to data used in stad arrow, in plot-arrow-ave eliminated other sizes, and labeling and also updated time_map plotting Tested everything on quipu.
added some time plots to paper Tested everything on node21.

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-stad/plots/ave-time/plot-time-averaged-arrow-300-1600-NflD-stad-25-400-150-0-1500-full_array}
  \caption{Arrow plots of our stadium shape}
  \label{stadium-arrow}
\end{figure}

@@

%% \begin{figure}
%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-1400-94-stoch}
%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-1860-94-stoch}
%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-2500-94-stoch}
%%   \caption{Arrow plots of our randst shape}
%%   \label{stadium-arrow}
%% \end{figure}

>>>>

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-stad/plots/plot-time-averaged-arrow-500-520-NflD-stad-25-400-150-0-1500-full_array}
  \caption{Arrow plots of our stadium shape}
  \label{stadium-arrow}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-stad/plots/time-map-NflD-stad-25-600-200-0-1500-full_array}
  \includegraphics[width=\columnwidth]{../data/shape-stad/plots/time-map-NflD-stad-25-400-150-0-1500-full_array}
  \caption{Time map plots of our stad shape}
  \label{time-maps-stad}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-NflD-randst-25-1850-1850-9500-1500-full_array}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-NflD-randst-25-2500-2500-9500-1500-full_array}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-NflD-randst-25-1860-2860-9400-1500-full_array}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-NflD-randst-25-2300-3200-9400-1500-full_array}
  \caption{Time map plots of our randst shape}
  \label{time-maps-randst}
\end{figure}
